### 2024-07-25 modern-portfolio-theory.qmd
20240724 - duplicate section labels
20240724 - add package to function call

### Determine the Efficient Frontier {#sec-efficientFrontier}

```{r}
efficientFrontier <- portfolioFrontier(
  returns_ts,
  spec = portfolioSpec)

@@

#### Portfolio with Max Return at a Given Risk Level {#sec-tangencyPortfolio}

>>>>

### Determine the Efficient Frontier {#sec-determineEfficientFrontier}

```{r}
efficientFrontier <- fPortfolio::portfolioFrontier(
  returns_ts,
  spec = portfolioSpec)

@@

#### Portfolio with Max Return at a Given Risk Level {#sec-maxReturnPortfolio}
